Fully Automatic Loop-free Program Synthesis by Bounded Model Checking

### 2014-01-28 paper/paper.tex
Fix bad hbox

We add a well-formedness constraint of the form \verb|params[i] <= (a + c + 2*i)|
for each instruction.  It should be noted that this requires a linear number of well-formedness
constraints.  If all of these constraints are satisfied, the program is well-formed in the sense
of Defn.~\ref{defn:well-formed}.

@@

\subsection{Experimental Results and Analysis}
The results of our experiments are shown in Fig.~\ref{fig:results-table}.
Column 1 shows the runtime reported for each benchmark in \cite{brahma}, column 2
shows the number of instructions in the synthesised program, and column 3 contains a \xmark when
{\sc Brahma} needed user assistance to solve a benchmark.
Columns 4 through 7 show the same information, but with the data taken from~\cite{brahma-icse}.
Column 5 shows the runtimes for the version of {\sc Brahma} from~\cite{brahma-icse} which
implemented the semibiased optimisation.
Finally, column 8 shows the runtime for {\sc Kalashnikov} and column 9 the number of instructions
in the program synthesised by {\sc Kalashnikov}.  The results can be broadly divided into
three categories, as follows:

>>>>

We add a well-formedness constraint of the form \verb|params[i] <= (a+c+2*i)|
for each instruction.  It should be noted that this requires a linear number of well-formedness
constraints.  If all of these constraints are satisfied, the program is well-formed in the sense
of Defn.~\ref{defn:well-formed}.

@@

\subsection{Results and Analysis}
The results of our experiments are shown in Fig.~\ref{fig:results-table}.
Column 1 shows the runtime reported for each benchmark in \cite{brahma}, column 2
shows the number of instructions in the synthesised program, and column 3 contains a \xmark\,when
{\sc Brahma} needed user assistance to solve a benchmark.
Columns 4 through 7 show the same information, but with the data taken from~\cite{brahma-icse}.
Column 5 shows the runtimes for the version of {\sc Brahma} from~\cite{brahma-icse} which
implemented the semibiased optimisation.
Finally, column 8 shows the runtime for {\sc Kalashnikov} and column 9 the number of instructions
in the program synthesised by {\sc Kalashnikov}.  The results can be divided into
three categories, as follows:
